\Title

### 2021-01-06 manuscript/manuscript.tex
Use only the source layouts figure
The figure with just the block average sketch wasn't necessary since the
one with all layouts has all the same information (the blocks and the
median position inside them).

@@

\begin{enumerate}
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region at a constant depth. A padding region is often added to help
    reduce edge effects. In practice, it often leads to underdetermined problems
    since a large number of sources is required ($N<M$).
  \item
    \emph{Sources below data points}: one equivalent source is placed below each
    observation point at a given depth (often dependent on the distance to
    neighboring data points). Therefore, the number of sources is be equal to
    the number of observations ($N=M$).
\end{enumerate}

For ground surveys, the \emph{regular-grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources-below-data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.
But when applied to airborne surveys, the \emph{source-below-data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when griding airborne
magnetic data.
In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

We propose a new way of distributing equivalent sources horizontally that could
simultaneously reduce the computational load and mitigate some of the drawbacks
of existing layouts.
In the \emph{block-averaged sources} layout,
point sources are placed in the average
position of data points that fall within specified spatial blocks
(Fig.~\ref{fig:block-averaged-sources}).
This is done by:

@@

Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
observation points that simulates a ground survey, and the possible location of
sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
averaged sources} and (d) the \emph{grid sources} layouts.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-averaged-sources-schematics.pdf}
    \caption{
        Block averaged sources.
        (a)~Given a set of observation points
        (b)~we divide the survey region on blocks of equal size and compute the
            median location of the observation points that fall inside each
            block.
        (c)~A source point is located beneath each block averaged coordinate.
            The number of point sources could be less or equal to the number of
            observation points. No source is located beneath unpopulated
            blocks.
    }
    \label{fig:block-averaged-sources}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources below data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Sketch of different horizontal layouts for equivalent source models.
        Blue points represent the locations of observations and orange points
        represent the locations of equivalent sources according to different
        layout strategies.
        (a) Set of \SourceLayoutsSchematicsObservations{} observation points
        that simulate a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
        obtained through the \emph{sources-below-data} layout.
        (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
        obtained through the \emph{regular-grid} layout.
        (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
        sources obtained through the \emph{block-averaged sources} layout.
    }
    \label{fig:source_layouts}
\end{figure*}

@@

\begin{enumerate}
  \item
    \emph{Sources below data points}: one equivalent source is placed at the
    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
    Therefore, the number of sources is be equal to the number of observations
    ($N=M$).
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
    added to help reduce edge effects. In practice, it often leads to
    underdetermined problems since a large number of sources is required
    ($N<M$).
\end{enumerate}

For ground surveys, the \emph{regular-grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources-below-data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.
But when applied to airborne surveys, the \emph{sources-below-data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when griding airborne
magnetic data.
In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

We propose a new way of distributing equivalent sources horizontally that could
simultaneously reduce the computational load and mitigate some of the drawbacks
of existing layouts.
In the \emph{block-averaged sources} layout,
point sources are placed in the average
position of data points that fall within specified spatial blocks
(Fig.~\ref{fig:source_layouts}d).
This is done by:

@@
